%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Professional experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Software Engineer} % Job title
{\href{https://www.fccn.pt/en/}{FCCN}, Foundation for Science and National Computing} % Organization
{Lisbon, Portugal} % Location
{Novembre 2016 - present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Software engineer in the Portuguese web archive. Responsible for indexing the web collected contents. Development of an image search prototype on archived pages. Implementation and reactivation of SonarQube for software Quality Control. Improve quality ranking of full text search.}
\item {Technologies: Java 8, eclipse, Spring boot, Json, Sublime, SonarQube, Hadoop, Apache Lucene, Solr, Github, CentOS, Python, Shell Scripting.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Software Engineer} % Job title
{Findmore} % Organization
{Lisbon, Portugal} % Location
{Novembre 2015 - Novembre 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item { \textbf{\href{http://www.universia.pt/}{UNIVERSIA} (Education)}}
\begin{itemize}
\item {Creation of an application  prototype  regarding  football tickets  online sales.
Responsible for developing Full-Stack web application in a team of two people. The application was developed in Angularjs + Spring Boot. Version control: github. Quality Control of the code: SonarQubue. Development flow management: Trello.
}
\item {Technologies: AngularJS, HTML5, Bootstrap, CSS3, Spring boot, Java, Github, Trello, SonarQube, Eclipse IDE.}
\end{itemize}
\item { \textbf{\href{https://www.santandertotta.pt/pt_PT/Particulares.html}{Santander Totta} (Bank)}}
\begin{itemize}
\item {Responsible for developing the functionality of a KPI generation web application from the consolidated data of Iberian Reporting. More specifically: implementation of a functional diagram editor whose output data are SQL commands.}
\item {Technologies: Java, Primefaces, Javascript, Jquery, Oracle SQL, Web Serive Rest, Apache POI.}
\end{itemize}
\item { \textbf{\href{https://www.realnetworks.com/}{Real Networks} (Telecommunications)}}
\begin{itemize}
\item {Resolution of scalable tickets. Changing several Web applications. Especially the creation of security filters to prevent different types of attacks, creation of features in a web application; a jukebox of personalized waiting music to the customer's choice for calls waiting, integration of the Oauth system in a Web application.}
\item {Technologies: Java, JSP, Spring Batch, Maven, HTML5, CSS3,  Solaris}
\end{itemize}
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Software Engineer} % Job title
{Coswichted} % Organization
{Lisbon, Portugal} % Location
{February 2015 - November 2015} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item { \textbf{\href{https://www.nos.pt/}{NOS} (Telecommunications)}}
\begin{itemize}
\item {Scalable and corrective maintenance of multi-domain projects (Marketing, Operations, Billing). Responsible for the API (PRO * c and PL / SQL) for the general client maintenance. Creation of electronic invoice archiving system (Java).}
\item {Technologies: Pro*C, Java, Oracle, SQL developer, Unix}
\end{itemize}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Software Engineer} % Job title
{Altran Portugal} % Organization
{Lisbon, Portugal} % Location
{September 2014 - February 2015} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item { \textbf{\href{https://www.iefp.pt/}{IEFP} (Institute for Employment and Training)}}
\begin{itemize}
\item {Scalable and corrective maintenance. Development of a PL / SQL APIs to support billing teams. Development of SOAP web services for the official website of the Institute for Employment and Vocational Training (IEFP).}
\item{Technologies: PL/SQL, PL/SQL Developer, Oracle 10g, SQL Developer, Java, Eclipse, SOAP, XML, Soapui, Linux.}
\end{itemize}
\end{cvitems} 
}

%------------------------------------------------

\cventry
{Developer Intern} % Job title
{\href{http://www.edp.pt/pt/Pages/homepage.aspx}{EDP} Commercial (Energy)} % Organization
{Coimbra, Portugal} % Location
{July 2013 - November 2013} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Implementation of new Web platform for management of unregulated market offers containing bid management options, list / edit / delete, and options to upload excel files import / export of all these offers; also Back-end responsible for data maintenance. This platform had two profiles: administrator and user.}
\item{Technologies: PHP, Bootstrap, jquery, Phpmyadmin, Notepad++, Mysql.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Trainee in training context} % Job title
{\href{https://www.ipn.pt/}{Instituto Pedro Nunes} (Business incubator)} % Organization
{Coimbra, Portugal} % Location
{May 2010 - July 2010} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Implementation of a ticket application where users can accompany the status of requests and communicate by chat with the administrators.}
\item{Technologies: PHP, CSS, Phpmyadmin, Notepad++, Mysql, Linux.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Trainee in training context} % Job title
{\href{https://www.ipn.pt/}{Instituto Pedro Nunes} (Business incubator)} % Organization
{Coimbra, Portugal} % Location
{May 2009 - July 2009} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Maintenance of the institute's networks. Installing and configuring servers.}
\item{Technologies: Linux(Fedora, Ubuntu, Debian, OpenBSD), Servidor DNS, Email server, Firewall.}
\end{cvitems}
}

%------------------------------------------------



\end{cventries}
